New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2023-01-11 paper/paper.Rmd
fixed textcolor error

\textcolor{blue}{The Mathematica implementation relies on the inbuilt Mathematica function  `LocatorPane`. This function creates a region on the screen where the position of the mouse is captured and then converted to input that updates the graphics functions, enabling the manual navigation of the tour. We then use the graphics function `ListPlot` embedded in dynamic objects via  `DynamicModule` to produce the display. Control objects, such as sliders, locator panes, and input fields, are used on dynamic variables, and when there is a change in the dynamic variable the dynamic objects which contain that variable will be updated.

Di will explain what part and why is difficult in R, also check grammar}

>>>>

\textcolor{blue}{The Mathematica implementation relies on the inbuilt Mathematica function  `LocatorPane`. This function creates a region on the screen where the position of the mouse is captured and then converted to input that updates the graphics functions, enabling the manual navigation of the tour. We then use the graphics function `ListPlot` embedded in dynamic objects via  `DynamicModule` to produce the display. Control objects, such as sliders, locator panes, and input fields, are used on dynamic variables, and when there is a change in the dynamic variable the dynamic objects which contain that variable will be updated.}

\textcolor{blue}{Di will explain what part and why is difficult in R, also check grammar}

### 2023-01-11 paper/paper.tex
fixed textcolor error

\textcolor{blue}{The Mathematica} implementation relies on the inbuilt
Mathematica function \texttt{LocatorPane}. This function creates a
region on the screen where the position of the mouse is captured and
then converted to input that updates the graphics functions, enabling
the manual navigation of the tour. We then use the graphics function
\texttt{ListPlot} embedded in dynamic objects via \texttt{DynamicModule}
to produce the display. Control objects, such as sliders, locator panes,
and input fields, are used on dynamic variables, and when there is a
change in the dynamic variable the dynamic objects which contain that
variable will be updated.

Di will explain what part and why is difficult in R, also check
grammar\}

>>>>

\textcolor{blue}{The Mathematica implementation relies on the inbuilt Mathematica function  `LocatorPane`. This function creates a region on the screen where the position of the mouse is captured and then converted to input that updates the graphics functions, enabling the manual navigation of the tour. We then use the graphics function `ListPlot` embedded in dynamic objects via  `DynamicModule` to produce the display. Control objects, such as sliders, locator panes, and input fields, are used on dynamic variables, and when there is a change in the dynamic variable the dynamic objects which contain that variable will be updated.}

\textcolor{blue}{Di will explain what part and why is difficult in R, also check grammar}
